---
title: "DV_RProject1"
author: "Ronly Leung, Karen Lee"
date: "September 15, 2015"
output: html_document
---

```{r message = FALSE}
require("jsonlite")
require("RCurl")
require(extrafont)
require(ggplot2)
```

## Data Frames

### Data Frame using SQL query "select * from titanic"
```{r}
##source("C:/Users/ronly_000/Documents/utaustin/2015_fall/cs329e_elements_of_data_vis/DataVisualization/DV_RProject1/DV_RProject1/01 Data/DF_1.R", echo = TRUE)
source("../01 Data/DF_1.R", echo = TRUE)
```

### Data Frame using SQL query "select * from titanic where sex is not null"
```{r}
##("C:/Users/ronly_000/Documents/utaustin/2015_fall/cs329e_elements_of_data_vis/DataVisualization/DV_RProject1/DV_RProject1/01 Data/DF_2.R", echo = TRUE)
source("../01 Data/DF_2.R", echo = TRUE)
```

### Data Frame using SQL query "select * from titanic where age <= 10"
```{r}
##source("C:/Users/ronly_000/Documents/utaustin/2015_fall/cs329e_elements_of_data_vis/DataVisualization/DV_RProject1/DV_RProject1/01 Data/DF_3.R", echo = TRUE)
source("../01 Data/DF_3.R", echo = TRUE)
```

### Data Frame using SQL query "select * from titanic where age > 50"
```{r}
##source("C:/Users/ronly_000/Documents/utaustin/2015_fall/cs329e_elements_of_data_vis/DataVisualization/DV_RProject1/DV_RProject1/01 Data/DF_4.R", echo = TRUE)
source("../01 Data/DF_4.R", echo = TRUE)
```


## Visualization 1

```{r}
source("../02 Visualizations/DV_1.R", echo = TRUE)
```

* SQL Query: select * from titanic  
* This visualization shows each passenger's fare based on his/her age and sex (sex can be null).

## Visualization 2

```{r}
source("../02 Visualizations/DV_2.R", echo = TRUE)
```

* SQL Query: select * from titanic where sex is not null  
* This visualization shows each passenger's fare based on his/her age and sex (sex can't be null).

## Visualization 3

```{r}
source("../02 Visualizations/DV_3.R", echo = TRUE)
```

* SQL Query: select * from titanic where sex is not null  
* This visualization shows whether each passenger survived or not vs their fare, with the x-axis separated by sex.

## Visualization 4

```{r}
source("../02 Visualizations/DV_4.R", echo = TRUE)
```

* SQL Query: select * from titanic where sex is not null  
* This visualization categorizes passengers by class and survival status, resulting in 6 different graphs. Each graph plots fare to sex. 

## Visualization 5

```{r}
source("../02 Visualizations/DV_5.R", echo = TRUE)
```

* SQL Query: select * from titanic where age <= 10  
* This visualization also categorizes passengers, 10 years and younger, by class and survival status, resulting in 6 different graphs. Each graph plots fare to sex. 

## Our Own Creation!

```{r}
source("../02 Visualizations/DV_6.R", echo = TRUE)
```

* SQL Query: select * from titanic where age > 50  
* This visualization compares the age and survival status of passengers over the age of 50. The graph separates the passengers by sex.

