---
title: "DV_RProject1"
author: "Ronly Leung, Karen Lee"
date: "September 15, 2015"
output: html_document
---

```{r message = FALSE}
require("jsonlite")
require("RCurl")
require(extrafont)
require(ggplot2)
```

## Data Frames
``` {r}
df1 <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from titanic"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_kwl377', PASS='orcl_kwl377', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))
head(df1)
summary(df1)

df2 <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from titanic where sex is not null"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_kwl377', PASS='orcl_kwl377', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))
head(df2)
summary(df2)

df3 <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from titanic where age <= 10"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_kwl377', PASS='orcl_kwl377', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))
head(df3)
summary(df3)

df4 <- data.frame(fromJSON(getURL(URLencode('129.152.144.84:5001/rest/native/?query="select * from titanic where age > 50"'),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_kwl377', PASS='orcl_kwl377', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE), ))
head(df4)
summary(df4)
```

## Visualization 1
```{r}
ggplot() + 
  coord_cartesian() + 
  scale_x_continuous() +
  scale_y_continuous() +
  labs(title='Titanic') +
  labs(x="Age", y=paste("Fare")) +
  layer(data=df1, 
        mapping=aes(x=suppressWarnings(as.numeric(as.character(AGE))),y=suppressWarnings(as.numeric(as.character(FARE))), color=SEX), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        position=position_jitter(width=0.3, height=0)
  )
```

SQL Query: select * from titanic  
This visualization shows each passenger's fare based on his/her age and sex (sex can be null).

## Visualization 2
```{r}
ggplot() + 
  coord_cartesian() + 
  scale_x_continuous() +
  scale_y_continuous() +
  labs(title='Titanic') +
  labs(x="Age", y=paste("Fare")) +
  layer(data=df2, 
        mapping=aes(x=suppressWarnings(as.numeric(as.character(AGE))), y=suppressWarnings(as.numeric(as.character(FARE))), color=SEX), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        position=position_jitter(width=0.3, height=0)
  )
```

SQL Query: select * from titanic where sex is not null  
This visualization shows each passenger's fare based on his/her age and sex (sex can't be null).

## Visualization 3
```{r}
ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  labs(title='Titanic') +
  labs(x="SURVIVED", y=paste("FARE")) +
  layer(data=df2, 
        mapping=aes(x=SEX, y=as.numeric(as.character(FARE)), color=as.character(SURVIVED)), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        position=position_jitter(width=0.3, height=0)
  )
```

SQL Query: select * from titanic where sex is not null  
This visualization shows whether each passenger survived or not vs their fare, with the x-axis separated by sex.

## Visualization 4
```{R}
ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  facet_grid(PCLASS~SURVIVED, labeller=label_both) +
  labs(title='Titanic') +
  labs(x="SURVIVED", y=paste("FARE")) +
  layer(data=df2, 
        mapping=aes(x=as.character(SEX), y=as.numeric(as.character(FARE)), color=SEX),
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        position=position_jitter(width=0.3, height=0)
  )
```

SQL Query: select * from titanic where sex is not null  
This visualization categorizes passengers by class and survival status, resulting in 6 different graphs. Each graph plots fare to sex. 

## Visualization 5
```{r}
ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  facet_grid(PCLASS~SURVIVED, labeller=label_both) +
  labs(title='Titanic where age <= 10') +
  labs(x="SURVIVED", y=paste("FARE")) +
  layer(data=df3, 
        mapping=aes(x=as.character(SEX), y=as.numeric(as.character(FARE)), color=SEX),
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        position=position_jitter(width=0.3, height=0)
  )
```

SQL Query: select * from titanic where age <= 10  
This visualization also categorizes passengers, 10 years and younger, by class and survival status, resulting in 6 different graphs. Each graph plots fare to sex. 

## Our Own Creation!
```{r}
ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_continuous() +
  labs(title='Titanic where age > 50') +
  labs(x="SURVIVED", y=paste("AGE")) +
  layer(data=df4, 
        mapping=aes(x=SEX, y=as.numeric(as.character(AGE)), color=as.character(SURVIVED)), 
        stat="identity", 
        stat_params=list(), 
        geom="point",
        geom_params=list(), 
        position=position_jitter(width=0.3, height=0)
  )
```

SQL Query: select * from titanic where age > 50  
This visualization compares the age and survival status of passengers over the age of 50. The graph separates the passengers by sex.

